### 2018-01-25 Paper/jaccardbaetica.tex
add text dissimilarity

We analysed a dataset of 990 stamps from 81 workshops. From the dataset, a sample of 131 different stamps were identified and collected from from CEIPAC database (citar). The workshops were located in different locations in Baetica province, along the river Guadalquivir and its tributary Genil in order to detect similarities between stamps from workshops and spatial distance. The chronology in the workshops is widely diverse from I-III B.C. However, some stamps show a more specific chronology while the majority of them display a large activity of production being difficult to specify an accurate chronology. A reason can be that most of them were partially excavated focused on archaeological surveys to collect the maximum stamps as possible (CITAR)

@@

The dataset was analysed using a statistic method as Jaccard distance. This method allows to measure the dissimilarity between sets. In our case, Jaccard distance was used to calculate the mutual presence of traits in the stamps. A comparison was done with the distance of the workshops to know whether there was an association between stamps and spatial distance.

@@

This method was performed to measure the overlap between different samples of sets \citep{horn_measurement_1966}. Unlike Jaccard distance, Morisita-Horn variant can be used to handle large samples with different sizes and diversity. In our case, our dataset shows a sample not uniform so this method is useful when sets show a diversity amongst samples.

%escribir un poco más 
The index can be described  where 0 is no presence of overlap and 1 totally similarity. 
%hablar sobre Horn (Morisita)hablar sobre que el sample no estaba uniforme por eso usamos el morisita horn

@@

>>>>

We analysed a dataset of 990 stamps from 81 workshops. From the dataset, a sample of 131 different stamps were identified and collected from from CEIPAC database (citar). The workshops were situated in different locations in Baetica province, along the river Guadalquivir and its tributary Genil in order to detect similarities between stamps from workshops and spatial distance. The chronology in the workshops is widely diverse from I-III B.C. However, some stamps show a more specific chronology while the majority of them display a large activity of production being difficult to specify an accurate chronology. A reason can be that most of them were partially excavated focused on archaeological surveys to collect the maximum stamps as possible (CITAR)

@@

The dataset was analysed using a statistic method as Jaccard distance. This method allows to measure the dissimilarity by calculating the presence of sets (CITAR). In our case, Jaccard distance was used to compute the mutual presence of traits in the amphora stamps but it does not consider the number of absences. A comparison was done with the distance of the workshops to identify whether there was an association between stamps and spatial distance amongst workshops.

%indicar si se usa en archaeology el jaccard distance

@@

As a complement of Jaccard distance, we use the statistical technique Morisita-Horn index. Unlike Jaccard distance, this method was performed to measure the overlap between different samples of sets \citep{horn_measurement_1966}. In ecology, it describes the dissimilarity between the system of two communities.

Considering our dataset as non-uniform sample, this method provides a useful tool to handle large samples with different sizes and diversity. Index can be describe considering 0 as no presence of similarity of stamps and 1 a totally similarity between stamps.

%hablar sobre Horn (Morisita)hablar sobre que el sample no estaba uniforme por eso usamos el morisita horn

@@

No similarity between stamps and amphora workshops were founded.

\section{Acknowledgements}

The research was funded by European Research Council Advanced Grant
EPNet (340828).
